\section{About Kandria}
In the not too distant future, an accidental discovery leads humanity to reach the singularity: the creation of fully sentient androids that can act and think on their own. However, not long after the first few androids are deployed across the world, calamity strikes. In an instant, the surface world is obliterated. Cities, entire countries wiped from the face of the earth. \\

Some decades later, small settlements of survivors have started to emerge. Some of them try to reclaim and rebuild the ruins of former cities, fighting off the blazing sunlight and harsh sandstorms. Others take their chances underground, living in the vast catacombs and tunnels left over from the old world. Rabid animals, hostile robots, and looters make traversing unknown territory risky, and few manage survive in these harsh conditions. \\

You wake up in a pile of rubble, somewhere deep underground. A bright flashlight blinding your eyes amidst the darkness. As your eyes adjust you can make out two figures standing over you. One of them shouts ``Cath, I think I got it working!'' \\

\vskip1cm

Kandria is a 2D hack and slash platformer, set in a dreary post apocalyptic environment. You take on the role of a lone android and join a small group of survivors. In order to help them out you are sent on a variety of missions to explore, gather, and fight. Along this journey you are confronted with various ethical questions about transhumanism and the treatment of androids. \\

Kandria features a solid platforming experience to make exploration challenging and fun, and intermixes this with fast hack and slash action segments to break up the flow. A complex dialogue system allows for deep story delivery, characterisation, and player expression. The world and characters are illustrated with hand drawn and animated pixel art.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "pitch"
%%% TeX-engine: luatex
%%% End:
