\section{Budget \& Planning}
The following budget is for the entire game production. Pre-production is planned to take another 3-4 months, with production starting sometime in Summer 2020. After that the expected production time is one year. \\

\begin{tabularx}{\textwidth}{>{\rowmac}l>{\rowmac}R<{\clearrow}}
  \textbf{Expenses} &\\
  Preproduction &\\
  \quad Core developer \& artist & 8'000 \\
  \quad Steam publishing & 100 \\
  Production &\\
  \quad Core developer \& artist & 24'000 \\
  \quad Additional artist & 6'000 \\
  \quad Music \& SFX & 10'000 \\
  \quad Writing & 1'000 \\
  \quad Marketing & 10'000 \\
  \hline\noalign{\vskip 0.1cm}
  \setrow{\bfseries} Total & \color{red}59'100 \\
  \noalign{\vskip 1cm}
  
  \textbf{Contributions} &\\
  Funding &\\
  \quad Personal investment & 10'000 \\
  \quad Pro Helvetia grant & 15'000 \\
  Release &\\
  \quad Steam Sales & 50'000 \\
  \hline\noalign{\vskip 0.1cm}
  \setrow{\bfseries} Total & \color{OliveGreen}75'000 \\
  \noalign{\vskip 1cm}

  \hline\hline\noalign{\vskip 0.1cm}
  \setrow{\bfseries} Cumulative Total & \color{OliveGreen}15'900\\
\end{tabularx}

\clearpage
\subsection{Market Research and Projected Sales}
The game will primarily target medium to experienced players with interest in a 2D pixel art style, and the platforming and hack and slash gameplay genres. The primary storefront will be Steam, which already features many similar games, though very few with an explicit focus on exploration and narrative delivery, which should help Kandria stand out. \\

The estimated sales of similar games in these genres vary greatly between lesser known titles such as The Moonstone Equation selling about 500 units, and bigger hits such as ICEY selling around 500'000 units. Based on these and other games found on Steam, the estimated sales number lies somewhere between 2'000 and 10'000 units. With a standard price tag of 10.-, this should result in anywhere between 13'000 to 66'000 in revenue after the storefront cut and taxes.

% NAME                          PRICE    SALES LINK
% Tagged: 2D & Hack and Slash
% ICEY                           11.- ~500'000 https://store.steampowered.com/app/553640/ICEY/
% They Bleed Pixels              10.-  ~50'000 https://store.steampowered.com/app/211260/They_Bleed_Pixels/
% The Dishwasher: Vampire Smile  10.-  ~25'000 https://store.steampowered.com/app/268990/The_Dishwasher_Vampire_Smile/
% Armed With Wings               15.-  ~10'000 https://store.steampowered.com/app/340580/Armed_with_Wings_Rearmed/
% Rain Blood Miracles: Mirage    10.-   ~5'000 https://store.steampowered.com/app/240660/Rain_Blood_Chronicles_Mirage/

% Tagged: 2D & Exploration
% VVVVVV                          5.- ~250'000 https://store.steampowered.com/app/70300/VVVVVV/
% Timespinner                    20.-  ~36'000 https://store.steampowered.com/app/368620/Timespinner/
% Wenjia                         10.-   ~5'000 https://store.steampowered.com/app/933450/Wenjia/
% The Moonstone Equation         10.-     ~500 https://store.steampowered.com/app/589100/The_Moonstone_Equation/

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "pitch"
%%% TeX-engine: luatex
%%% End:
