\section{Future Development}
Since the game is still in its early stages there is naturally a lot that's left to be done. Currently in progress is a much more elaborate animation system to support the hack and slash mechanics, as well as a dedicated editor to fine tune the animation and attack parameters. Once that is complete, an NPC behaviour system needs to be implemented to allow for interesting enemies. Once these features are worked out, the core mechanics for the game should be in place. From there the engine work would mostly include quality of life improvements to speed up the content pipeline. \\

For the visuals most of the work is left in designing the various enemy types and support characters, as well as ultimately animating all necessary moves. Currently at least three main cast characters, three supporting characters, and four types of enemies are planned, though this might have to expand even further depending on the story development. Several new tilesets for the areas covered by the story also need to be made, once it is clearer what the overall story will be like. \\

As mentioned, the story and overall writing will require a lot of attention quite soon. The decisions made for that will also greatly influence the amount of work left in other areas. Certain narrative moments could require additional mechanics to be implemented, as well.

\subsection{Grant Use}
The money for the grant would primarily be used to support myself, as I can cover a large set of roles required for the game already. However, with enough funding the development speed could be increased tremendously by distributing the animation, environment art, and writing work onto additional people. Whatever the case, I will definitely need to hire people to handle the music and sound design of the game, as these are areas where I lack sufficient experience.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "pitch"
%%% TeX-engine: luatex
%%% End:
