\section{Current Status}
Proper development on the game started in Summer of 2019. The game is built upon a custom in-house engine called \href{https://shirakumo.org/trial}{Trial}. This gives large productivity boosts in some areas, since complete knowledge of the engine allows very fast, targeted development. However, in other areas development has been very slow, since solutions need to be built from the ground up. Being a one-man team at the moment also means that every part of the game takes away time from others.\\

At the time of writing, the game has the following features fully implemented:

\begin{itemize}
\item \textbf{2D Platformer Mechanics}\quad
  The player has full 2D movement on sloped terrain, including wall jumps, climbing, crawling, dashing, and moving platforms.
\item \textbf{Dynamic Lighting System}\quad
  A dynamic lighting system with shadows and a day/night cycle has been implemented to paint the proper mood in various environments.
\item \textbf{Efficient Tilemap Rendering}\quad
  The game implements a technique to render tilemaps of arbitrary size at constant overhead, allowing for very big maps.
\item \textbf{In-Game Editor}\quad
  The in-game editor allows creating and editing maps directly while the game is running, making for a very quick feedback loop.
\item \textbf{Platform Traversal AI}\quad
  The engine is able to automatically move characters across arbitrary 2D terrain just as the player would, making it possible to conveniently script characters to move around.
\item \textbf{Dialogue System}\quad
  A custom markup language was implemented to allow writing dynamic dialogue trees quickly and efficiently. The system is even capable of scripting cutscenes.
\item \textbf{}\quad
\end{itemize}

This sets a solid precedent for building most of the game. There are a few important features that are still missing, which are discussed in the next section.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "pitch"
%%% TeX-engine: luatex
%%% End:
