\section{Future Development}\label{sec:future}
We are nearing the completion of the vertical slice. This has given us a good idea on the required effort for a large section of the game. As a next step we are intending on completing the first half of the first act of the game, which includes the game's introduction and tutorial. In order to do so we'll also have to further polish and refine the existing mechanics and assets, and develop the first few custom music tracks.

This first half can then be used as marketing material by publishing it on Steam as a free ``First Act Demo''. This should help grow our community and gather general interest in the project. We can further use the demo as pitching material for grant applications and other investment opportunities.

From there the plan is to develop a horizontal slice -- laying out all the areas and story beats in broad strokes, to give us a better idea of the overall length of the game and its flow. We are aiming for a 10-12 hour playtime in total, and putting together the horizontal slice should give us a much better idea of how much content we can cut or have to expand on. It should also help a lot to settle the overall story structure and build towards a pleasing tension arc.

After the slice is completed and tested, we can then move on to fleshing it out, chapter by chapter, building up to a complete product. Finally, the last half year should be spent testing, polishing, and refining the game to make it as good as can be.

\subsection{Investment Use}
Money from investment would primarily be put to use to avoid having to cut features from the game and to expand its budget for music, sound, and ultimately marketing, which should help a lot to increase the value of the game and ensure its success.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "pitch"
%%% TeX-engine: luatex
%%% End:
